Exp. 2 Analysis: 2AFC, adults vs. children

### 2020-09-01 analysis/exp2_analysis.Rmd
updated analysis of children's Exp 2 data and comparison to model and adult data

---
title: "Exp. 2 Analysis: 2AFC, adults vs. children"
author: "George"
date: Sys.Date()
output: html_document
---

```{r libraries}
knitr::opts_chunk$set(echo = TRUE)

@@

```{r load-model-data, include=F}
mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
mdat <- read_csv("agent-data/curiodrop_0.csv") # most trials close to chance
mdat <- read_csv("agent-data/curiodrop_1.csv")
mdat <- read_csv("agent-data/curiodrop_2.csv")

@@

mdat %>% group_by(drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target), n=n())

@@

```{r load-human-data, include=FALSE}
raw = read.csv2("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv", sep=',', header=F, stringsAsFactors = F)
# row 1 is empty, row 2 should be header
d = raw[4:nrow(raw),]
names(d) = raw[2,]
d[,"NA"] = NULL
# duplicate column names
#names(d)[13]
#names(d)[21]

@@

# Q38-Q41 = which toy did you just drop? (catch trials)
#d = d %>% select(-Q38, -Q39, -Q40, -Q41, -Q42, -Q43) # duplicate column names
d$Q11 = NULL
d$Q38 = NULL
d$Q39 = NULL
d$Q40 = NULL
d$Q41 = NULL
d$Q42 = NULL
d$Q43 = NULL
d$`Random ID` = NULL
d$`Duration (in seconds)` = "Duration"
#write.csv(d, file="exp2_cleaned.csv")
```

```{r}
rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
rawch[which(is.na(rawch$Exclude)),]$Exclude = 'N'

@@

# make long
#cdl <- cd %>% pivot_longer()

# first 10 columns are

for(i in 3:ncol(cd)) {
  tt = table(cd[,i])
  bt = binom.test(tt, p=.5, alternative="two.sided")
  cat(names(cd)[i], ' ', sum(tt), ' p=', round(bt$p.value,3))
  print(round(tt / sum(tt), 2))
}

# Octahedron   39  p= 0.003
#   pyramid trig prism 
#      0.74       0.26 
# Pentagon   41  p= 0.001
#    bowl pentagon 
#    0.76     0.24 
# Pyramid   41  p= 0.06
# octahedron      torus 
#      0.34       0.66 
# Dumbbell_1   42  p= 0.02
#      bowl octahedron 
#      0.69       0.31 
```

```{r}
hist(cd$Age)
```

```{r}

```

>>>>

---
title: "Exp. 2 Analysis: 2AFC, adults vs. children"
author: "George & Sama"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, echo=F}
knitr::opts_chunk$set(echo = F, warning=F)

@@

# Load Model Data

This is preliminary, not final model data.

```{r load-model-data}
mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
mdat <- read_csv("agent-data/curiodrop_0.csv") # most trials close to chance
mdat <- read_csv("agent-data/curiodrop_1.csv")
mdat <- read_csv("agent-data/curiodrop_2.csv")

@@

model_trial_agg <- mdat %>% group_by(drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target), n=n())

@@

# Load Adult Data

```{r load-human-data, include=F, echo=FALSE}
raw = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
# row 1 is empty, row 2 should be header
d = raw[3:nrow(raw),]
names(d) = raw[1,]
d[,"NA"] = NULL
names(d) <- make.unique(names(d))
d[which(is.na(d$Exclude)),]$Exclude = 'N'

@@

# Q38-Q41 = which toy did you just drop? (catch trials)
d = d %>% 
  dplyr::select(-Q11, -Q38, -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>%
  rename(Duration = `Duration (in seconds)`)
#write.csv(d, file="exp2_cleaned.csv")

Nsubj = length(unique(d$ResponseId))
# shown 1 object to drop, choose which target
adult_long <- d %>%
  pivot_longer(cols = 9:29,
                   names_to = "drop",
                   values_to = "choice",
                   values_drop_na = FALSE) %>%
    mutate(drop = tolower(drop)) %>%
    mutate(drop = case_when(
      drop=="torus.1" ~ "torus",
      drop=="cone.1" ~ "cone",
      drop=="pyramid.1" ~ "pyramid",
      drop=="dumbbell.1" ~ "dumbbell",
      drop=="octahedron.1" ~ "octahedron",
      drop=="pipe.1" ~ "pipe",
      drop=="trig prism.1" ~ "trig prism",
      drop=="pentagon.1" ~ "pentagon",
      drop=="sphere.1" ~ "sphere",
      drop=="bowl.1" ~ "bowl",
      drop=="torus.2" ~ "torus",
      TRUE ~ drop
    )) %>% mutate(Trial = rep(1:21, Nsubj)) %>% 
  mutate(
    target = rep(c("pentagon", "pipe", "cone", "cone", "pyramid", "pipe", "bowl", "bowl", "bowl", "torus", "torus",
               "bowl", "pentagon", "trig prism", "torus", "pentagon", "pipe", "trig prism", "pentagon", "pipe", "torus"), Nsubj), # matches relation (containment/support)
    relation = rep(c("support", rep("contain", 10), rep("support", 10)), Nsubj) #c(rep(, 10), rep( , 10))
  ) %>% 
  mutate(chose_target = ifelse(choice == target, 1, 0)) %>%
  filter(Trial!=1, Exclude!='Y') # remove training trial

adult_trial_agg <- adult_long %>% group_by(drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

# maybe look at Duration distribution at some point
```
At a trial level, are the adults' and model's choices correlated?

```{r adult-model-correlation}
# model vs. adult (trial level)
cor.test(adult_trial_agg$chose_target, model_trial_agg$chose_target)
```

# Load Child Data

```{r load-child-data}
rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
rawch[which(is.na(rawch$Exclude)),]$Exclude = 'N'

@@

# make long
Nsubj_ch = length(unique(cd$ID))
# shown 1 object to drop, choose which target
ch_long <- cd %>%
  pivot_longer(cols = 4:23,
                   names_to = "drop",
                   values_to = "choice",
                   values_drop_na = FALSE) %>%
    mutate(drop = tolower(drop)) %>%
    mutate(drop = case_when(
      drop=="torus_1" ~ "torus",
      drop=="cone_1" ~ "cone",
      drop=="pyramid_1" ~ "pyramid",
      drop=="dumbbell_1" ~ "dumbbell",
      drop=="octahedron_1" ~ "octahedron",
      drop=="pipe_1" ~ "pipe",
      drop=="trig prism_1" ~ "trig prism",
      drop=="pentagon_1" ~ "pentagon",
      drop=="sphere_1" ~ "sphere",
      drop=="bowl_1" ~ "bowl",
      TRUE ~ drop
    )) %>% mutate(Trial = rep(1:20, Nsubj_ch)) %>% 
  mutate(
    target = rep(c("pipe", "cone", "cone", "pyramid", "pipe", "bowl", "bowl", "bowl", "torus", "torus",
               "bowl", "pentagon", "trig prism", "torus", "pentagon", "pipe", "trig prism", "pentagon", "pipe", "torus"), Nsubj_ch), # matches relation (containment/support)
    relation = rep(c(rep("contain", 10), rep("support", 10)), Nsubj_ch) #c(rep(, 10), rep( , 10))
  ) %>% 
  mutate(chose_target = ifelse(choice == target, 1, 0))

child_trial_agg <- ch_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

cor.test(child_trial_agg$chose_target, adult_trial_agg$chose_target)

trial_tab <- child_trial_agg %>% select(-n) %>% 
  bind_cols(adult_target_choice = adult_trial_agg$chose_target) %>% 
  rename(child_target_choice = chose_target) %>%
  bind_cols(model_target_choice = model_trial_agg$chose_target)
# t(18) = 2.42 p=.03 r=.50

#for(i in 3:ncol(cd)) {
#  tt = table(cd[,i])
#  bt = binom.test(tt, p=.5, alternative="two.sided")
#  cat(names(cd)[i], ' ', sum(tt), ' p=', round(bt$p.value,3))
#  print(round(tt / sum(tt), 2))
#}

# Octahedron   39  p= 0.003
#   pyramid trig prism 
#      0.74       0.26 
# Pentagon   41  p= 0.001
#    bowl pentagon 
#    0.76     0.24 
# Pyramid   41  p= 0.06
# octahedron      torus 
#      0.34       0.66 
# Dumbbell_1   42  p= 0.02
#      bowl octahedron 
#      0.69       0.31 
knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)
```

## Compare Children's and Adults' Relational Choices

```{r compare-children-and-adults}
pos = position_dodge(width = .9)

adult_long <- adult_long %>% rename(ID = ResponseId) %>%
  mutate(Age = "adult") %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target)

combo_dat <- ch_long %>% mutate(ID = as.character(ID),
                                Age = as.character(Age)) %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target) %>%
  bind_rows(adult_long) %>% 
  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))

combo_dat %>% group_by(ID, AgeGroup, relation) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
  group_by(relation, AgeGroup) %>%
  tidyboot_mean(chose_target) %>%
  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic()
```

Still collecting data:

```{r}
hist(cd$Age, main="")
```
